Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-03-15 analysis/paper/paper.Rmd
Remove TOC from PDF
Clean up extra spaces in code
Remove code comment

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(ggExtra)
library(dplyr)
library(stringr)
```

>>>>

library(bookdown)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(ggExtra)
library(dplyr)
library(stringr)
```
